\documentclass[a4paper,12pt]{article}
\usepackage{graphicx}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}
\geometry{margin=1in}
\titleformat{\section}{\Large\bfseries}{\thesection}{1em}{}
\pagestyle{fancy}
\lhead{Fingerprint Lock System Manual}
\rhead{University of Basel}

\title{\textbf{Fingerprint Lock System Manual}}
\author{\textit{Valerio Job, Luca Faessler, Barththan Sivanantham}}
\date{\today}

\begin{document}
\maketitle

\section{Introduction}
This project, developed for the Computer Architecture lecture at the University of Basel, integrates multiple components to provide secure access control. This system provides a robust and secure method for access control. With PIN and fingerprint authentication, users can effectively manage entry permissions while ensuring security.

\section{System Overview}
\subsection{Components}
\begin{itemize}
    \item \textbf{LCD Display:} Displays system messages and prompts.
    \item \textbf{Fingerprint Sensor:} Allows fingerprint enrollment and authentication.
    \item \textbf{Keypad:} Enables PIN entry and menu navigation.
\end{itemize}

\subsection{Operating Modes}
\begin{enumerate}
    \item \textbf{Default Mode:} Displays the current time and options to access the menu or unlock the door.
    \item \textbf{Menu Mode:} Allows the user to perform administrative tasks like managing fingerprints and changing PINs.
\end{enumerate}

\section{System Setup}
\subsection{Powering the System}
\begin{enumerate}
    \item Connect the 12V power supply to the power socket.
    \item Ensure all components are properly wired.
\end{enumerate}

\subsection{Initializing the System}
Upon startup, the system will:
\begin{itemize}
    \item Display an initialization message.
    \item Connect to the Wi-Fi network.
    \item Synchronize the time via an NTP server.
\end{itemize}

\section{Functionalities}
\subsection{Unlocking the Door}
\begin{itemize}
    \item Press \# on the keypad.
    \item Authenticate via fingerprint within allowed hours (8 AM – 8 PM).
    \item If a registered fingerprint is matched, the door will unlock.
\end{itemize}

\subsection{Menu Access}
\begin{itemize}
    \item Press * to enter the menu.
    \item Enter the master PIN (default: 9999).
    \item Navigate through options for fingerprint management and PIN changes.
\end{itemize}

\subsection{Menu Functionalities}
\begin{itemize}
    \item \textbf{Fingerprint Management:}
    \begin{itemize}
        \item Add Fingerprint
        \item Remove Fingerprint
    \end{itemize}
    \item \textbf{Change PIN:}
    \begin{itemize}
        \item Enter current PIN
        \item Set a new PIN
    \end{itemize}
    \item \textbf{Exit Menu:} Press * to return to the main screen.
\end{itemize}

\section{Error Handling}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Error Message} & \textbf{Cause} & \textbf{Solution} \\
\hline
No Match Found & Fingerprint not recognized & Try again, enroll if necessary \\
Wrong PIN & Incorrect PIN entered & Re-enter the correct PIN \\
WiFi Connecting & Wi-Fi connection issue & Check SSID and password \\
Timeout & No fingerprint detected within time & Place the finger correctly \\
\hline
\end{tabular}


\end{document}
